Intentional release of native species undermines ecological stability

### 2022-03-14 rmd/manuscript.Rmd
edit: minor

@@

# Acknowledgments

@@

# Competing interests

None declared.

# **Data and materials availability**

@@

\newpage

>>>>

**Authors:** Akira Terui^1\*^, Hirokazu Urabe^2^, Masayuki Senzaki^3^, Bungo Nishizawa^4^

**\*Corresponding author:** hanabi0111\@gmail.com

**Affiliations:** ^1^ Department of Biology, University of North Carolina at Greensboro, Greensboro, NC 27412, USA ^2^ Salmon and Freshwater Fisheries Research Institute, Hokkaido Research Organization, Eniwa, Hokkaido, 061-1433, Japan ^3^ Faculty of Environmental Earth Science, Hokkaido University, Sapporo, Hokkaido, 060-0810, Japan ^4^ National Institute of Polar Research, Tachikawa, Tokyo, 190-8518, Japan

@@

# Acknowledgements

@@

# Competing interest

None declared

# Data availability

@@
